Supplementary Materials from: \textit{Innovation and elaboration on the avian tree of life}; Science Advances, in review

### 2023-06-08 Manuscript/supplementaries.tex
Fix long table
Update supplementaries.tex

\usepackage[margin=2cm]{geometry}
\usepackage{lscape}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[osf]{mathpazo}
\usepackage{fullpage}
\usepackage{float}
\usepackage{ltablex}

@@

\begin{figure}[H]
\centering
   \includegraphics[width=0.9\textwidth]{Figures/axis_selection.pdf}
\caption{Variance and cumulative variance for each of the eight principal component (PC) axes for each super-order. Note that not all super-orders have their own variance explained matching the variance explained by the entire ordination. For example, Strisores only need the first three dimensions to explain at least 95\% of their variance within the shapespace whilst Aequornithes need all eight dimensions to achieve at least the same amount of variance explained.}
\label{Fig:axes_variance}
\end{figure}

@@

\begin{figure}[H]
\centering
   \includegraphics[width=0.5\textwidth]{Figures/parameters_ESS_passeriformes.pdf}
\caption{Histogram of the effective sample sizes (ESS) for each class of parameters in the MCMCglmm model for the passeriformes for the 4000 posteriors. \textbf{solutions} is the solution of the model; \textbf{Gcovariances} is the covariance for the random terms (the phylogeny and the clades); \textbf{Rcovariances} is the residual error term.}
\label{Fig:model_ess_passeriformes}
\end{figure}

@@

\input{Tables/tab_ortho_results.tex}

@@

\begin{figure}[H]
\centering
   \includegraphics[width=1\textwidth]{Figures/ellipses_passeriformes.pdf}
\caption{\textbf{(A)} Ellipses representing the scaled average posterior evolutionary rate matrix from the pGLMM models for each passeriformes sub-orders and families (coloured ellipses) compared to the passeriformes phylogenetic component of the models (grey ellipses).
We scaled the ellipses so the length of the phylogenetic major axis of beak variation of the clade ellipse is the same length as that of the passeriformes phylogenetic major axis ellipse (in eight dimensions).
The first inset ellipse plot shows the positions of all sub-order ellipses relative to the passeriformes phylogenetic ellipse.
Subsequent inset plots show the results for each sub-order. 
Inset bar plots show the proportion of variance associated with each of the eight principal component (PC) axes in shapespace.
The inset boxplots correspond to the $elaboration_{clade}$ (left) and $innovation_{clade}$ (right) scores for all 4000 posterior samples.
The dots represent the median $elaboration_{clade}$ and $innovation_{clade}$ values while the thick and dashed lines represent the 50\% and 95\% confidence intervals respectively.
These scores were calculated on the unscaled ellipses resulting in different scales of $elaboration_{clade}$ and $innovation_{clade}$ for each plot.
\textbf{(B)} Results for each families.}
\label{fig_ellipses_passeriformes}
\end{figure}

>>>>

\usepackage[margin=2cm]{geometry}
\usepackage{lscape}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[osf]{mathpazo}
\usepackage{fullpage}
\usepackage{float}
\usepackage{ltablex}
\usepackage{longtable}
\usepackage[tablewithin=none,figurewithin=none,singlelinecheck=false]{caption}

@@

 % GT Figure legend needs explanation of whole_space and no_calde
\begin{figure}[H]
\centering
   \includegraphics[width=0.9\textwidth]{Figures/axis_selection.pdf}
\caption{Variance and cumulative variance for each of the eight principal component (PC) axes for each super-order. Note that not all super-orders have their own variance explained matching the variance explained by the entire ordination. For example, Strisores only need the first three dimensions to explain at least 95\% of their variance within the shapespace whilst Aequornithes need all eight dimensions to achieve at least the same amount of variance explained.}
\label{Fig:axes_variance}
\end{figure}

@@

\begin{figure}[H]
\centering
   \includegraphics[width=0.5\textwidth]{Figures/parameters_ESS_passeriformes.pdf}
\caption{Histogram of the effective sample sizes (ESS) for each class of parameters in the MCMCglmm model for the Passeriformes for the 4000 posteriors. \textbf{solutions} is the solution of the model; \textbf{Gcovariances} is the covariance for the random terms (the phylogeny and the clades); \textbf{Rcovariances} is the residual error term.}
\label{Fig:model_ess_passeriformes}
\end{figure}

@@

\begin{landscape}
\input{Tables/tab_ortho_results.tex}
\end{landscape}

@@

\begin{figure}[H]
\centering
   \includegraphics[width=1\textwidth]{Figures/ellipses_passeriformes.pdf}
\caption{\textbf{(A)} Ellipses representing the scaled average posterior evolutionary rate matrix from the pGLMM models for each Passeriformes sub-orders and families (coloured ellipses) compared to the Passeriformes phylogenetic component of the models (grey ellipses).
We scaled the ellipses so the length of the phylogenetic major axis of beak variation of the clade ellipse is the same length as that of the Passeriformes phylogenetic major axis ellipse (in eight dimensions).
The first inset ellipse plot shows the positions of all sub-order ellipses relative to the Passeriformes phylogenetic ellipse.
Subsequent inset plots show the results for each sub-order. 
Inset bar plots show the proportion of variance associated with each of the eight principal component (PC) axes in shapespace.
The inset boxplots correspond to the $elaboration_{clade}$ (left) and $innovation_{clade}$ (right) scores for all 4000 posterior samples.
The dots represent the median $elaboration_{clade}$ and $innovation_{clade}$ values while the thick and dashed lines represent the 50\% and 95\% confidence intervals respectively.
These scores were calculated on the unscaled ellipses resulting in different scales of $elaboration_{clade}$ and $innovation_{clade}$ for each plot.
\textbf{(B)} Results for each families.}
\label{fig_ellipses_passeriformes}
\end{figure}
